### 2020-03-10 thesis_template/2_RelatedWork/model/spark.tex
added GC tuning section

\begin{itemize}
    \item GC tuning solutions
    \item Annotation, off-heap solution 
\end{itemize}

>>>>

\section{Garbage Collection Tuning}
\label{sec:history}
Several solutions are suggested. Main idea is to reduce number of object and execution of GC. 
One is avoiding pointer-based data structures, such as HashMap and LinkedList. These objects have a "wrapper" object for each entry 
so that number of object tends to be larger than when when an array is used. Caching serialized object in memory also reduce number of object and memory usage 
since the set of objects become a byte array. In addition, developers can allocate byte array off-heap of JVM to avoid tracking by GC. 
Although these memory management solution for GC help developer improve performance of Spark applications, the effort to discover the best GC tuning afflicts developers.
